%-------------------------
% Resume in Latex
% Author : Diego Lopes
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://example.com/}{\Large Diego Lopes do Nascimento}} & Email : \href{diego.lopes.2402@gmail.com}{diego.lopes.2402@gmail.com}\\
  \href{https://github.com/diegoldnascimento}{https://github.com/diegoldnascimento} & Mobile : \href{tel:+5521994647682}{+55-21-99464-7682} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {PUC-Rio - Pontifícia Universidade Católica do Rio de Janeiro}{Rio de Janeiro, Brazil}
      {Postgraduate Degree in Computer Software Engineering}{Jan. 2023 -- Jan. 2024}
    \resumeSubheading
      {Universidade Estácio de Sá}{Rio de Janeiro, Brazil}
      {Bachelor of Computer Information Systems}{2012 -- 2016}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
%-----------PROJECTS----------------\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Hona}{Current Location}
      {Staff Software Engineer}{Present}
      \resumeItemListStart
        \resumeItem{Impact-Driven Development}
          {Responsible for identifying points of improvement and helping the company and other teams to scale the Hona Client and Hona App product.}
      \resumeItemListEnd

\resumeSubheading
      {Route}{Remote}
      {Staff Software Engineer}{Feb 2024 - Jul 2024}
      \resumeItemListStart
        \resumeItem{Impact-Driven Development}
          {Spearheaded initiatives that significantly increased revenue by 20\%, improved key metrics, and reduced churn risk from several clients, positively impacting Series C funding, which reached \$40 million.}
        \resumeItem{Front-End Architecture}
          {Designed and built scalable front-end architectures using React and Web Components to ensure smooth integration and a great user experience across different platforms.}
 \resumeItem{E-commerce Integrations}
          {Implemented seamless integrations with major e-commerce platforms such as Shopify, BigCommerce, WooCommerce, and Amazon, ensuring compatibility with our internal API architecture to enhance the insurance purchase experience for merchants and consumers.}
        \resumeItem{Team Leadership and Mentorship}
          {Guided and mentored team members, fostering a collaborative environment that promotes learning and technical growth.}
        \resumeItem{Project Documentation}
          {Maintained detailed and up-to-date documentation, including technical specs, project briefs, and specific technical documents to support ongoing and future projects.}
        \resumeItem{Development Best Practices}
          {Promoted best practices in the Software Development Life Cycle (SDLC) by implementing tools and technologies like Docker, CI/CD pipelines, Terraform, and AWS infrastructure.}
        \resumeItem{Testing Frameworks}
          {Led the adoption of Test-Driven Development (TDD) and Behavior-Driven Development (BDD) frameworks using tools like Testing Library, Jest, Nightmare, and Cypress to ensure reliable code.}
        \resumeItem{API and Microservices Design}
          {Designed and managed APIs and microservices using a range of AWS services, such as ECS, RDS, DynamoDB, Redis, SSM, SQS, CloudWatch, S3, and CloudFront, all managed through Infrastructure-as-Code (IaC).}
        \resumeItem{Delivering Solutions}
          {Led the creation and deployment of solutions that improved the insurance purchase process, driving customer satisfaction and operational efficiency.}
      \resumeItemListEnd

  \resumeSubheading
      {Route}{Remote}
      {Senior Software Engineer}{Sep 2021 - Feb 2024}
      \resumeItemListStart
        \resumeItem{User Interface Architecture}
          {Coded and designed the architecture for the widgets user interface written in React, implemented on multiple platforms such as Shopify, BigCommerce, WooCommerce, and Magento, to deliver a best-in-class insurance purchase experience for consumers and merchants.}
        \resumeItem{Project Documentation}
          {Wrote and maintained up-to-date documentation of projects, including technical specifications, 6-pagers, and specific documentation when needed.}
        \resumeItem{Front-End Architecture}
          {Designed scalable front-end architectures using React and Web Components for applications across multiple platforms.}
        \resumeItem{Development Best Practices}
          {Drove the SDLC process culture of best practices by implementing Docker, CI/CD deployments, Terraform, and Amazon AWS architecture across multiple projects.}
        \resumeItem{Testing Frameworks}
          {Drove and implemented TDD or BDD testing frameworks, such as Testing Library, Jest, Nightmare, and Cypress, for unit, integration, and end-to-end testing across multiple projects.}
        \resumeItem{API and Microservices Design}
          {Designed APIs or Microservices that manage a majority of Amazon AWS services, such as ECS, RDS, DynamoDB, Redis, SSM, Amazon SQS, CloudWatch, S3, and CloudFront, managed through Infrastructure-as-Code.}
        \resumeItem{Mentoring and Coaching}
          {Mentored and coached team members to help and inspire them with technology topics.}
      \resumeItemListEnd

  \resumeSubheading
      {ThoughtLab}{Remote}
      {Mid-Senior Software Engineer}{Mar 2019 - Aug 2019}
      \resumeItemListStart
        \resumeItem{WordPress Development}
          {Provided top-notch support and maintenance for PHP and WordPress projects by utilizing best practices to develop highly customizable WordPress themes from scratch.}
        \resumeItem{Plugin Customization}
          {Coded and customized WordPress plugins while integrating with the WooCommerce plugin, ensuring seamless performance.}
        \resumeItem{Mobile Project Support}
          {Offered exceptional maintenance and support for mobile projects developed using Ionic 2 and Firebase, ensuring they operated smoothly.}
        \resumeItem{WooCommerce Development}
          {Developed WooCommerce themes from scratch and provided payment gateway integration support, thus ensuring enhanced user experience.}

         \resumeItem{E-commerce Integrations}
          {Implemented seamless integrations with major e-commerce platforms such as Shopify, BigCommerce, WooCommerce, and Amazon, ensuring compatibility with our internal API architecture to enhance the insurance purchase experience for merchants and consumers.}
      \resumeItemListEnd

    \resumeSubheading
      {A Figueira}{Rio de Janeiro, Brazil}
      {Mid-Senior Software Engineer}{Mar. 2016 - Mar. 2017}
      \resumeItemListStart
        \resumeItem{Mobile App Development}
          {Developed and maintained a high-performance mobile app for Android and iOS using the Ionic framework, achieving over 100,000 downloads and a 4.5-star rating.}
        \resumeItem{PHP and WordPress Projects}
          {Supported and developed features for PHP and WordPress projects, including custom themes and plugins.}
      \resumeItemListEnd

    \resumeSubheading
      {Lar Fabiano de Cristo}{Rio de Janeiro, Brazil}
      {Associate Software Developer / Junior Software Engineer}{Aug. 2012 - Feb. 2016}
      \resumeItemListStart
        \resumeItem{Web Development}
          {Developed and maintained web applications, improving user experiences and functionalities.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Typescript Clean Architecture API Boilerplate}
      {Open source Clean Architecture API to facilitate building up new APIs by using Clean Architecture Software Design}
  \resumeSubHeadingListEnd

\end{document}

